seqwish: inducing pangenome graphs

### 2021-12-04 manuscript/main.tex
add `-k0` in the workflow; draft the abstract

    \title[seqwish: very large variation graph inducer]{seqwish: very large variation graph inducer}
    \author[Garrison \textit{et~al}.]{
        Erik~Garrison\,$^{\text{\sfb 1} \dagger*}$
    }

@@

    \corresp{$^\ast$To whom correspondence should be addressed. \\
        $^\dagger$Contributed equally.}

@@

    \abstract{
        \textbf{Motivation:}
        ...  \\
        \textbf{Results:}
        We wrote seqwish, a novel tool to build a pangenome graph from a set of sequences and alignments between them. \\
        \textbf{Availability:}
        seqwish is published as free software under the MIT open source license.
        Source code and documentation are available at \url{https://github.com/ekg/seqwish}.
        seqwish can be installed via Bioconda \url{https://bioconda.github.io/recipes/seqwish/README.html} or GNU Guix \url{https://github.com/ekg/guix-genomics/blob/master/seqwish.scm}. \\
        \textbf{Contact:} \href{egarris5@uthsc.edu}{egarris5@uthsc.edu} \\
%\textbf{Supplementary information:} Supplementary data are available at \textit{Bioinformatics} online.
    }

>>>>

    \title[seqwish: inducing pangenome graphs]{seqwish: inducing pangenome graphs}
    \author[Garrison \textit{et~al}.]{
        Erik~Garrison\,$^{\text{\sfb 1}*}$
    }

@@

    \corresp{
        $^\ast$To whom correspondence should be addressed. \\
       % $^\dagger$Contributed equally.\
    }

@@

    \abstract{
        \textbf{Motivation:}
        Pangenome graphs provide a complete representation of the mutual alignment of collections of genomes.
        One of its most common forms is the variation graph model.
        A set of pairwise alignments imply a variation graph, but, to our knowledge, there are no methods to generate such a graph or lossless string graph from these alignments.\\
        \textbf{Results:}
        We wrote seqwish, a novel tool to induce a variation graph from a set of sequences and alignments between them.
        seqwish operates in external memory, by conversion of the alignment set into an alignment graph and the subsequent
        use of this graph in the elaboration of the variation graph including paths representing the input sequences.
        The resulting graph is a lossless representation of the input and its alignments.\\
        \textbf{Availability:}
        seqwish is published as free software under the MIT open source license.
        Source code and documentation are available at \url{https://github.com/ekg/seqwish}.
        seqwish can be installed via Bioconda \url{https://bioconda.github.io/recipes/seqwish/README.html} or GNU Guix \url{https://github.com/ekg/guix-genomics/blob/master/seqwish.scm}. \\
        \textbf{Contact:} \href{egarris5@uthsc.edu}{egarris5@uthsc.edu} \\
%\textbf{Supplementary information:} Supplementary data are available at \textit{Bioinformatics} online.
    }
